On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-22 paper/paper.tex
wibble

The Feldspar project~\cite{Axelsson:10:Feldspar,Axelsson,Svenningsson:13:Combining}
is a Haskell embedding of a monadic interface
that targets C, and focuses on high-performance. Interestingly, this work
also attempt to make use of both deep and shallow embeddings inside a single
implementation. Both Feldspar and and our work use some form
of monadic reification technology~\cite{Persson:11:MonadicDSL,Svenningsson:13:Compositional,Sculthorpe:13:ConstrainedMonad}.

>>>>

The Feldspar project~\cite{Axelsson:10:Feldspar,Axelsson,Svenningsson:13:Combining}
is a Haskell embedding of a monadic interface
that targets C, and focuses on high-performance. Interestingly, this work
also attempts to make use of both deep and shallow embeddings inside a single
implementation. Both Feldspar and our work use some form
of monadic reification technology~\cite{Persson:11:MonadicDSL,Svenningsson:13:Compositional,Sculthorpe:13:ConstrainedMonad}.
